COG-ED Manuscript

### 2021-12-10 06_Paper/COG-ED/Manuscript.Rmd
some improvements h2b

  knitr::opts_chunk$set(echo = TRUE)
  library(bibtex)
  library(here)         # to set a directory without defined paths, "here" package
  library(tidyverse)    # plotting and managing data, "tidyverse" package
  library(bayestestR)   # computing area under the curve, "bayestestR" package
  library(papaja)       # APA conform output, "papaja" package
  library(lmerTest)     # for multilevel modeling
  library(snow)         # for faster processing
  library(afex)         # compute repeated measures ANOVA, "afex" package
  library(emmeans)      # for custom contrasts in ANOVAs, "emmeans" package

@@

To determine the influence of task performance in the association of SVs and n-back level, we will set up a MLM using the $lmerTest$ package. 
We apply restricted maximum likelihood (REML) to fit the model.
First, we calculate the intraclass correlation (ICC) on the basis of the null model.
Second, we estimate a random slopes model of SV including n-back load level as level-1-predictor and, additionally, NFC as level-2-predictor. 
Within the model, we control for *d'*, RT, correct and post-correct trials.
$$
SV \sim level\ * NFC + d' + RT + correct + postcorrect + (level|subject)
$$
Level-1-predictors are centered within cluster, whereas the level-2-predictor is centered at the grand mean as recommended by Enders & Tofighi [-@Enders2007].
Third, we perform a simple slopes analysis with n-back level as predictor and NFC as moderator. 
# TODO: Johnson-Neyman plot

@@

  # detach afex in order to user lmerTest
  detach("package:afex", unload = TRUE)

@@

  agg_vars <- cbind(data_SV, dprime["d"])
  h2b_data <- merge(agg_vars, data_nback, by = c("subject", "level"))

@@

  # include new variable for post-correct trials
  h2b_data$postcorrect = rep(NA, length(h2b_data$correct))  # add empty column
  for (z in 1:(length(h2b_data$correct)-1)) {               # for all trials except the very last one
    if (h2b_data$correct[z] == 1) {                         # if correct, paste correct
      h2b_data$postcorrect[z+1] <- 1
    } else if (h2b_data$correct[z] == 0) {                  # if not correct, paste incorrect
      h2b_data$postcorrect[z+1] <- 0
    } else {
      h2b_data$postcorrect[z+1] <- NA                       # if empty, leave empty
    } 
  }

  # 512 trials, 8 blocks á 64 trials
  i <- 1
  while (i <= nrow(h2b_data)){
    for (j in 1:64) {
      h2b_data$trial <- seq(1, 64, 1)
    }
    i <- i + 64
  }

  h2b_data$postcorrect[h2b_data$trial == "1"] <- 1         # avoid transfer from previous block and subject (first trial of a block is always correct)

@@

  # d'
  h2b_sub$d.mwc <- ave(h2b_sub$d, h2b_sub$subject, FUN = function(x) mean(x, na.rm = T))
  h2b_sub$d.cwc <- h2b_sub$d - h2b_sub$d.mwc

  # RT
  h2b_sub$rt.mwc <- ave(h2b_sub$rt, h2b_sub$subject, FUN = function(x) mean(x, na.rm = T))
  h2b_sub$rt.cwc <- h2b_sub$rt - h2b_sub$rt.mwc

  # level
  h2b_sub$level.mwc <- ave(h2b_sub$level, h2b_sub$subject, FUN = function(x) mean(x, na.rm = T))
  h2b_sub$level.cwc <- h2b_sub$level - h2b_sub$level.mwc

  # correct 
  h2b_sub$correct.mwc <- ave(h2b_sub$correct, h2b_sub$subject, FUN = function(x) mean(x, na.rm = T))
  h2b_sub$correct.cwc <- h2b_sub$correct - h2b_sub$correct.mwc

  # postcorrect
  h2b_sub$postcorrect.mwc <- ave(h2b_sub$postcorrect, h2b_sub$subject, FUN = function(x) mean(x, na.rm = T))
  h2b_sub$postcorrect.cwc <- h2b_sub$postcorrect - h2b_sub$postcorrect.mwc

@@

  # null model -----------------------------------------------------------------
  m0_h2b <- lmer(sv ~ 1 + (1|subject), 
                 data = h2b_sub)

@@

  ## maximal model ---- 
  m1_h2b <- lmer(sv ~ level.cwc * nfc.cgm + d.cwc + rt.cwc + correct.cwc + postcorrect.cwc + (level.cwc|subject), 
                 data = h2b_sub,
                 REML = T) # parameters estimated by maximizing restricted log-likelihood

@@

  library(interactions)
  m1_h2b.ss <- sim_slopes(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none", 
                    cond.int = T,                                       # print conditional intercepts
                    johnson_neyman = T, jnplot = T, control.fdr = T)    # calculate Johnson Neyman intervals,

@@

  colnames(h2b_result.table)[1] <- "Parameter"
  colnames(h2b_result.table)[2] <- "Beta"
  colnames(h2b_result.table)[3] <- "SE"
  colnames(h2b_result.table)[4] <- "p-Value"
  colnames(h2b_result.table)[5] <- "Random Effects (SD)"

  row.names(h2b_result.table) <- NULL
  h2b_result.table$Parameter[1:8] <- c("Intercept", "N-Back Level", "NFC", "D-Prime", "RT", "Correct", "Post-Correct", "Level x NFC")
  # FIXME: display control variables? Spelling lower/upper case

@@

  h2b_result.table$`p-Value`[which(h2b_result.table$`p-Value`<.01)] <- 
    paste0(h2b_result.table$`p-Value`[which(h2b_result.table$`p-Value`<.01)],"*")
  h2b_result.table$`p-Value`[which(h2b_result.table$`p-Value`<.05)] <- 
    paste0(h2b_result.table$`p-Value`[which(h2b_result.table$`p-Value`<.05)],"*")
  h2b_result.table$`p-Value`[which(h2b_result.table$`p-Value`<.001)] <- 
    paste0("<.001***")

@@

@@

  m1_h2b.ss$slopes

@@

  # create interaction plot
  h2b_ssa.plot <- interact_plot(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none",
                                x.label = "n back load level", y.label = "subjective value",
                                legend.main = "NFC", interval = T) + theme_apa()

@@

simple slopes analysis `r h2b_ssa.table`, `r h2b_ssa.plot`
statistically significant influence of n-back load level on subjective value, but no moderating effect of NFC

>>>>

  knitr::opts_chunk$set(echo = TRUE)
  library(bibtex)
  library(here)         # to set a directory without defined paths, "here" package
  library(tidyverse)    # plotting and managing data, "tidyverse" package
  library(bayestestR)   # computing area under the curve, "bayestestR" package
  library(papaja)       # APA conform output, "papaja" package
  library(lmerTest)     # for multilevel modeling
  library(afex)         # compute repeated measures ANOVA, "afex" package
  library(emmeans)      # for custom contrasts in ANOVAs, "emmeans" package

@@

To determine the influence of task performance in the association of SVs and n-back level, we will set up a MLM using the $lmerTest$ package. 
We apply restricted maximum likelihood (REML) to fit the model.
First, we calculate the intraclass correlation (ICC) on the basis of the null model.
Second, we estimate a random slopes model of SV including n-back load level as level-1-predictor and, additionally, NFC as level-2-predictor. 
Within the model, we control for *d'*, RT, correct and post-correct trials.
$$
SV \sim level\ * NFC + d' + RT + correct + postcorrect + (level|subject)
$$
Level-1-predictors are centered within cluster, whereas the level-2-predictor is centered at the grand mean as recommended by Enders & Tofighi [-@Enders2007]. 
We visually inspect the residuals of the final model. The approximately normal distribution indicates no evidence to perform model criticism.  
Third, we perform a simple slopes analysis with n-back level as predictor and NFC as moderator. 
To evaluate the moderating effect, we calculate the Johnson-Neyman interval.

@@

  # detach afex in order to use lmerTest
  detach("package:afex", unload = TRUE)

@@

  h2b_data <- merge(dprime[c("subject", "level", "d")], data_nback, by = c("subject", "level"))

@@

@@

  # d'
  h2b_sub$d.cwc <- h2b_sub$d - (ave(h2b_sub$d, h2b_sub$subject, FUN = function(x) mean(x, na.rm = T)))

  # RT
  h2b_sub$rt.cwc <- h2b_sub$rt - (ave(h2b_sub$rt, h2b_sub$subject, FUN = function(x) mean(x, na.rm = T)))

  # level
  h2b_sub$level.cwc <- h2b_sub$level - (ave(h2b_sub$level, h2b_sub$subject, FUN = function(x) mean(x, na.rm = T)))

  # correct 
  h2b_sub$correct.cwc <- h2b_sub$correct - (ave(h2b_sub$correct, h2b_sub$subject, FUN = function(x) mean(x, na.rm = T)))

  # postcorrect
  h2b_sub$postcorrect.cwc <- h2b_sub$postcorrect - (ave(h2b_sub$postcorrect, h2b_sub$subject, FUN = function(x) mean(x, na.rm = T)))

@@

  # null model -----------------------------------------------------------------
  m0_h2b <- lmer(sv ~ 1 + (1|subject), 
                 data = h2b_sub,
                 REML = T)

@@

  ## maximal model ---- 
  m1_h2b <- lmer(sv ~ level.cwc * nfc.cgm + d.cwc + rt.cwc + correct.cwc + postcorrect.cwc + (level.cwc|subject), 
                 data = h2b_sub,
                 REML = T) # parameters estimated by restricted log-likelihood maximization

@@

@@

  colnames(h2b_result.table)[1] <- "Parameter"
  colnames(h2b_result.table)[2] <- "Beta"
  colnames(h2b_result.table)[3] <- "$SE$"
  colnames(h2b_result.table)[4] <- "$p$-value"
  colnames(h2b_result.table)[5] <- "Random Effects (SD)"

  row.names(h2b_result.table) <- NULL
  h2b_result.table$Parameter[1:8] <- c("Intercept", "N-Back Level", "NFC", "d'", "RT", "Correct", "Post-Correct", "Level x NFC")
  # FIXME: display control variables? Spelling lower/upper case

@@

  h2b_result.table$`$p$-value`[which(h2b_result.table$`$p$-value`<.01)] <- 
    paste0(h2b_result.table$`$p$-value`[which(h2b_result.table$`$p$-value`<.01)],"*")
  h2b_result.table$`$p$-value`[which(h2b_result.table$`$p$-value`<.05)] <- 
    paste0(h2b_result.table$`$p$-value`[which(h2b_result.table$`$p$-value`<.05)],"*")
  h2b_result.table$`$p$-value`[which(h2b_result.table$`$p$-value`<.001)] <- 
    paste0("<.001***")

@@

  library(interactions)
  m1_h2b.ss <- sim_slopes(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none", 
                    cond.int = T,                                       # print conditional intercepts
                    johnson_neyman = T, jnplot = T, control.fdr = T)    # calculate Johnson Neyman intervals,
                                                                        # create plot, adjust false discovery rate

  # save Johnson-Neyman plot
  h2b_jnplot <- m1_h2b.ss$jnplot

  # create interaction plot
  h2b_ssa.plot <- interact_plot(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none",
                                x.label = "n back level", y.label = "subjective value",
                                legend.main = "NFC", interval = T) + theme_apa()

@@

@@

@@

simple slopes analysis `r h2b_ssa.table`, `r h2b_jnplot`,`r h2b_ssa.plot`
statistically significant influence of n-back load level on subjective value, but no moderating effect of NFC
